 

### 2021-08-05 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd

**Authors:** 
Nidhi Vinod^1^,
Martijn Slot^2^,
Ian McGregor^3^,
Elsa M. Ordway^4^,
Marielle N. Smith^5^,
Tyeen Taylor,
Lawren Sack,
Kristina J. Anderson-Teixeira^1,2^*

@@

5. Department of Forestry, Michigan State University, East Lansing, MI 48824, USA

@@

![**Figure `r fig_leaf_T`. Theoretical expectations for variation in the elevation of $T_{leaf}$ above $T_{air}$ in response to (a) shortwave radiation, (b) wind speed, (c) relative humidity, (d) leaf width, and (e) stomatal conductance.** Leaf temperatures were modeled using the tealeaves R package of @muir_tealeaves_2019 parameterized to represent typical conditions for a broadleaf species (*Quercus rubra*) in a mesic temperate forest (Harvard Forest, Massachusetts, USA), as detailed in Appendix `r appendix_tealeaves_methods`. [ISSUE #6](https://github.com/EcoClimLab/vertical-thermal-review/issues/6).](leaf_energy_balance/leaf_energy_fig3.png)

>>>>

**Authors:** 
Nidhi Vinod^1^,
Martijn Slot^2^,
Ian McGregor^3^,
Elsa M. Ordway^4^,
Marielle N. Smith^6^,
Tyeen Taylor^7^,
Lawren Sack^5^,
Kristina J. Anderson-Teixeira^1,2^*

@@

5. Department of Ecology and Evolutionary Biology, UCLA, Los Angeles, CA 90039, USA

6. Department of Forestry, Michigan State University, East Lansing, MI 48824, USA

7. Department of Civil & Environmental Engineering, University of Michigan, Ann Arbor, MI 48109, USA

@@

![**Figure `r fig_leaf_T`. Theoretical expectations for variation in the elevation of $T_{leaf}$ above $T_{air}$ in response to (a) shortwave radiation, (b) wind speed, (c) relative humidity, (d) leaf width, and (e) stomatal conductance.** Leaf temperatures were modeled using the tealeaves R package of @muir_tealeaves_2019 parameterized to represent typical conditions for a broadleaf species (*Quercus rubra*) in a mesic temperate forest (Harvard Forest, Massachusetts, USA), as detailed in Appendix `r appendix_tealeaves_methods`. [ISSUE #6](https://github.com/EcoClimLab/vertical-thermal-review/issues/6).](leaf_energy_balance/fig3_leafenergy.png)
